---
title: "Structures and Dynamics on (of) Complex Networks (sdcn). I Ecosystems"
author: "Authors"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Structures and Dynamics on (of) Complex Networks (sdcn).
  I Ecosystems}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r set-options, echo=FALSE, cache=FALSE}
options(width=85)
```

The package intends to implement general simulation of dynamics on (of) networks
which have different structural features. The current goal is to simuate ecological interactions among species in ecological networks, as the first instance of complex networks.

Modules should include:

* Null models of different structural features such as degree heterogeneity and modularity.
* Dynamic models. Holling Type I, II dynamic models should be implemented for mutualistic networks, food webs, competitive networks, and mixed networks.
* Environmental Perturbations. Two types of perturbations: continuously pressed env. and repeated pulsed env. (stochastics). The perturbations can effect not only on (all or part of) species(nodes) but also on (all or part of) interactions(links).
* Analysis of simulation results. 
* Fit of empirical data?

## Null models of networks

### Degree Heterogeneity


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
